\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/related_work.tex

We summarize the former efforts on USB attacks and defenses in
Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of
each defense against various attacks including our \tool.

>>>>

We summarize the former efforts on USB attacks and defenses in
Table~\ref{table:attack_vs_defense}. \cite{usbkiller, cable,smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip} are not included in this table, because these works are all recovering or injecting signal on the physical layer, we only illustrate the effectiveness of 
each defense against various attacks, including our \tool, on the software layer in Table~\ref{table:attack_vs_defense}.
